\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-07-22 article.tex
\clearpage for layout

We can immediately see that Figure \ref{fig:plotTNBin6} more successfully mitigates text overlap compared to Figure \ref{fig:plotTNBin3}. We can also confirm what we saw in the previous plot that indeed most varieties were released between 1950 and 1970, and any textual overlap is confined to this range of years.

@@

The most novel visual function in \pkg{ggenealogy}, \code{plotAncDes()} allows users to view the ancestors and descendants of a given variety. The inputted variety is highlighted in the center of the plot, ancestors are displayed to the left of the center, and descendants are displayed to the right of the center. The further from the center that a variety is located, the more generations that variety is distanced from the centered variety of interest.

This particular \pkg{ggenealogy} tool is unique because most available genealogy and graph visualization software do not allow for repeated labels. It is a useful tool because, as was demonstrated in Figures \ref{fig:kinshipFig} and \ref{fig:Graph}, some genealogical datasets require repeated node labels if they are to be visualized by generation counts. Indeed, our example soybean genealogy is one such dataset.

@@

This generates the top plot of Figure \ref{fig:Lee}. We notice that \code{Lee} has 3 generations of ancestors and 5 generations of descendants. We also notice that some varieties are repeated in the plot, which is a unique feature provided by \pkg{ggenealogy}. For example, the variety \code{5601T} is represented four times - once as a third generation descendant of \code{Lee}, once as a fourth generation descendant of \code{Lee}, and twice as a fifth generation descendant of \code{Lee}. The variety \code{5601T} was repeated multiple times because there are multiple paths between \code{Lee} and \code{5601T}. For explanation purposes, all paths between \code{Lee} and \code{5601T} were manually highlighted in blue.

\begin{figure}[H]
    \centering
    \fbox{\includegraphics[width=\textwidth]{LeeAD}}
    \caption{Top: All ancestors and descendants of the variety \code{Lee} are shown in this \pkg{ggenealogy} plot. Bottom: This plot was constructed manually outside of the \pkg{ggenealogy} plot for didactic purposes. It mimics the blue paths in the \pkg{ggenealogy} plot on the top, only now nodes cannot be repeated. The parenthetical numbers above each node represents the set of generation counts that node is away from the center node \code{Lee}. The presence of red parentheses indicate that the plot on the bottom ambiguously display the example soybean genealogy in the way that the \pkg{ggenealogy} plot on the top can accomplish.}
    \label{fig:Lee}
\end{figure}

@@

\subsection{Plotting animation}
\label{interaction}

>>>>

We can immediately see that Figure \ref{fig:plotTNBin6} more successfully mitigates text overlap compared to Figure \ref{fig:plotTNBin3}. We also confirm what we saw in the previous plot that most varieties were released between 1950 and 1970, and any textual overlap is confined to this range of years.

@@

The most novel visual function in \pkg{ggenealogy}, \code{plotAncDes()} allows users to view the ancestors and descendants of a given variety. The inputted variety is highlighted in the center of the plot, ancestors are displayed to the left of the center, and descendants are displayed to the right of the center. The further from the center that a variety is located, the more generations that variety is distanced from the centered variety of interest. This particular \pkg{ggenealogy} tool is uniquely beneficial because most genealogy and graph visualization software do not allow for repeated node labels even though some genealogical datasets require repeated node labels in order to be visualized by generation counts (as was shown in Figures \ref{fig:kinshipFig} and \ref{fig:Graph}).

@@

This generates the top plot of Figure \ref{fig:Lee}. We notice that \code{Lee} has 3 generations of ancestors and 5 generations of descendants. We also notice that some varieties are repeated, which is a unique feature provided by \pkg{ggenealogy}. For example, the variety \code{5601T} is represented four times - once as a third generation descendant of \code{Lee}, once as a fourth generation descendant of \code{Lee}, and twice as a fifth generation descendant of \code{Lee}. The variety \code{5601T} was repeated multiple times because there are multiple paths between \code{Lee} and \code{5601T}. For explanation purposes, all paths between \code{Lee} and \code{5601T} were manually highlighted in blue.

\begin{figure}[H]
    \centering
    \fbox{\includegraphics[width=\textwidth]{LeeAD}}
    \caption{Top: All ancestors and descendants of the variety \code{Lee} are shown in this \pkg{ggenealogy} plot. Bottom: For didactic purposes, this plot was constructed manually outside of the \pkg{ggenealogy} package. It mimics the blue paths in the \pkg{ggenealogy} plot on the top, only now nodes cannot be repeated. The parenthetical numbers above each node represents the set of generation counts that node is away from the center node \code{Lee}. The presence of red parentheses indicate that the plot on the bottom ambiguously display the example soybean genealogy in the way that the \pkg{ggenealogy} plot on the top can accomplish.}
    \label{fig:Lee}
\end{figure}

@@

\subsection{Interactive plotting functions}
\label{interaction}
